The value of intermediation

### 2023-11-20 src/paper/theory.tex
Start working on many-sided weighted value

\begin{proof}[Proof of Proposition \ref{prop:one_sided_general}]
    First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
    Furthermore,
    \begin{align*}
        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) = \E[X_n].
    \end{align*}
    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Putting it together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) \\
        &= \lim_{n \to \infty} \E[X_n] \\
        &= \E[X] \\
        &= \int_0^1 f(t) \mathrm{d}G(t).
    \end{align*}
    Furthermore, if $G$ is differentiable, then
    \begin{align*}
        \int_0^1 f(t) \mathrm{d}G(t) = \int_0^1 g(t) f(t) \dt.
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop:many_sided_general}]
    The proof mirrors that of \cref{prop:one_sided_general}.
    First, note that the random order value can be expressed as follows:
    \begin{align*}
        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\mathcal{P}_P) = k_1, \dots, n_{A_L}(\mathcal{P}_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n X_n = (k_1, \dots, k_L)) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr \left( X_n = \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \right) f \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
        &= \E[f(X_n)].
    \end{align*}
    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Putting it together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L).
    \end{align*}
    Finally, if $X$ is a continuous random variable, then
    \begin{align*}
        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of Lemma \ref{lem:many_sided_manifold}]
    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
    \begin{align*}
        \varphi_P^n &= \E[f(X_n)].
    \end{align*}
    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Therefore,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
        &= \E[f(X)] \\
        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
    \end{align*}
\end{proof}

The Shapley-value:

@@

\begin{proof}[Proof of Proposition \ref{prop:many_sided_shapley}]
    Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.

@@

\begin{lemma}
    \label{lem:convergence_to_manifold}
    Consider the random vector $X_n$ with values from $[0, 1]^L$.
    Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$ where $h(s)$ is some continuous function.
    Let $S_n \xrightarrow[]{d} S$.
    Then $X_n \xrightarrow[]{d} h(S)$.
\end{lemma}

\begin{proof}[Proof of lemma \ref{lem:convergence_to_manifold}]
    We have to show that
    \begin{align*}
        \lim_{n \to \infty} \Pr(X_n \leq x) = \Pr(h(S) \leq x).
    \end{align*}
    for any $x$ where the cdf of $h(S)$ is continuous.

@@

    Let us start with the first term.
    \begin{align*}
        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S_n) \leq x) \right| \\
        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \mathrm{d}G_n(s) \right| \\
        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \mathrm{d}G_n(s) \right| \\
        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \mathrm{d}G_n(s) \right| \\
        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \mathrm{d}G(s) \\
        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \mathrm{d}G_n(s) - \int_0^1 r(s) \mathrm{d}G(s) \right| \\
        &= 0.
    \end{align*}
    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^2} h(s)$.
    The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.

@@

@@

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}[Proof of Lemma \ref{lemma:log_convergence}]
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
    Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$.
    Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.

@@

\begin{lemma}
    \label{lemma:integral_convergence}
    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly.
    Then,
    \begin{align*}
        \lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) = \int_0^1 f(t) \dt.
    \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma \ref{lemma:integral_convergence}]
    \begin{align*}
        &\lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) \\
        &= \lim_{n \to \infty} \frac{b-a}{n} \left[ \sum_{k=1}^n f \left( a + \frac{b-a}{n} \right) + \sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \right] \\
        &= \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left| f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right| \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right| \\
        &= \int_a^b f(t) \dt + (b-a) \underbrace{\lim_{n \to \infty} \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right|}_{=0 \text{ due to uniform convergence}} \\
        &= \int_a^b f(t) \dt
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of Proposition \ref{prop:monotone}]
    Monotonicity is evident.
    For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$.
    WLOG assume it is the latter, therefore $v(S_2) = 0$.
    As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:one_sided}]
    Let $R$ denote a permutation of the set of players ($N$).
    Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
    The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
    \begin{align*}
        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
    \end{align*}
    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
    Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
    More precisely, 
    \begin{align*}
        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
    \end{align*}
    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
    \begin{align*}
        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
    \end{align*}
    Putting all the above together, the value of player $P$ can be expressed as
    \begin{align*}
        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
    \end{align*}
    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$.
    Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
        &= \int_0^1 f(t) \dt .
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of Lemma \ref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
    The probability of $P$ having at most fraction $t$ of the other players before itself is
    \begin{align*}
        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
    \end{align*}
    Taking limits,
    \begin{align*}
        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    Let
    \begin{align*}
        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    By lemma \ref{lemma:log_convergence}, 
    \begin{align*}
        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
    \end{align*}
    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).

@@

\begin{proof}[Proof of Proposition \ref{prop:one_sided_weighted}]
    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
    \begin{align*}
        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
    \end{align*}
    As before, using the fact that fringe players are identical, this can be rephrased as
    \begin{align*}
        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
        &= \E[f(X_n / n)]
    \end{align*}
    where $X_n$ is defined as above.
    $f$ is continuous, and therefore bounded on the compact set $[0, 1]$.
    As a consequence, $\frac{X_n}{n} \xrightarrow[]{d} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 f(t) \mathrm{d}G(t) \\
        &= \int_0^1 g(t)f(t) \dt
    \end{align*}
    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
\end{proof}

>>>>

\begin{proof}[Proof of \cref{prop:one_sided_general}]
    First, observe that $f$ is continuous on the compact set $[0, 1]$, and is therefore also bounded.
    Furthermore,
    \begin{align*}
        \varphi_P^n = \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) = \E[X_n].
    \end{align*}
    As $f$ is continuous and bounded, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Putting it together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \frac{1}{n+1} \sum_{k=0}^n \Pr(|\mathcal{P}_P| / n = k) f(k/n) \\
        &= \lim_{n \to \infty} \E[X_n] \\
        &= \E[X] \\
        &= \int_0^1 f(t) \mathrm{d}G(t).
    \end{align*}
    Furthermore, if $G$ is differentiable, then
    \begin{align*}
        \int_0^1 f(t) \mathrm{d}G(t) = \int_0^1 g(t) f(t) \dt.
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of \cref{prop:many_sided_general}]
    The proof mirrors that of \cref{prop:one_sided_general}.
    First, note that the random order value can be expressed as follows:
    \begin{align*}
        \varphi_P^n &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n_{A_1}(\mathcal{P}_P) = k_1, \dots, n_{A_L}(\mathcal{P}_P) = k_L) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr(n X_n = (k_1, \dots, k_L)) f\left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
        &= \sum_{k_1=0}^n \dots \sum_{k_L=0}^n \Pr \left( X_n = \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \right) f \left(\frac{k_1}{n}, \dots, \frac{k_L}{n}\right) \\
        &= \E[f(X_n)].
    \end{align*}
    Furthermore, as $f$ is continuous (and therefore bounded on $[0, 1]^L$), and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Putting it together,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L).
    \end{align*}
    Finally, if $X$ is a continuous random variable, then
    \begin{align*}
        \int_0^1 \dots \int_0^1 f(t_1, \dots, t_L) \mathrm{d}G(t_1, \dots t_L) = \int_0^1\dots \int_0^1 g(t_1, \dots, t_L) f(t_1, \dots, t_L) \dt_1 \dots \dt_L.
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of \cref{lem:many_sided_manifold}]
    Just like in the proof of \cref{prop:many_sided_general}, the random order value can be expressed as follows:
    \begin{align*}
        \varphi_P^n &= \E[f(X_n)].
    \end{align*}
    Furthermore, as $f$ is continuous and bounded on $[0, 1]^L$, and $X_n \xrightarrow[]{d} X$, by Portmanteau's lemma, $\E[f(X_n)] \to \E[f(X)]$.
    Therefore,
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \E[f(X_n)] \\
        &= \E[f(X)] \\
        &= \E[f(a_1(\xi), \dots, a_L(\xi))] \\
        &= \int_0^1 f(a_1(s), \dots a_L(s)) \mathrm{d}H(s).
    \end{align*}
\end{proof}

\subsection{Shapley-value}

@@

\begin{proof}[Proof of \cref{prop:many_sided_shapley}]
    Let us show than $X_n$ converges in distribution to the degenerate random variable $X = (U, \dots, U)$, where $U$ is uniformly distributed on $[0, 1]$.

@@

\begin{lemma}
    \label{lem:convergence_to_manifold}
    Consider the random vector $X_n$ with values from $[0, 1]^L$.
    Let $S_n = \sum_l[X_n]_l / L$, with the cumulative distribution function $G_n(s)$.
    Assume that for every $s \in [0, 1]$, $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$ where $h(s)$ is some continuous function.
    Let $S_n \xrightarrow[]{d} S$.
    Then $X_n \xrightarrow[]{d} h(S)$.
\end{lemma}

\begin{proof}[Proof of \cref{lem:convergence_to_manifold}]
    We have to show that
    \begin{align*}
        \lim_{n \to \infty} \Pr(X_n \leq x) = \Pr(h(S) \leq x).
    \end{align*}
    for any $x$ where the cdf of $h(S)$ is continuous.

@@

    Let us start with the first term.
    \begin{align*}
        \lim_{n \to \infty} &\left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \Pr(h(S_n) \leq x) \right| \\
        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) \mathrm{d}G_n(s) - \int_0^1 \mathbf{1}[h(s) \leq s] \mathrm{d}G_n(s) \right| \\
        &= \lim_{n \to \infty} \left| \int_0^1 \Pr(X_n \leq x \mid S_n = s) - \mathbf{1}[h(s) \leq x] \mathrm{d}G_n(s) \right| \\
        &= \lim_{n \to \infty} \left| \int_0^1 \underbrace{\Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x]}_{\coloneqq r(s)} \mathrm{d}G_n(s) \right| \\
        &\leq \lim_{n \to \infty} \int_0^1 \left| \Pr(X_n \leq x \mid nS_n = \lfloor ns \rfloor) - \mathbf{1}[h(s) \leq x] \right| \mathrm{d}G(s) \\
        &+ \lim_{n \to \infty} \left| \int_0^1 r(s) \mathrm{d}G_n(s) - \int_0^1 r(s) \mathrm{d}G(s) \right| \\
        &= 0.
    \end{align*}
    The first limit is zero because $X_n \mid n S_n = \lfloor ns \rfloor \xrightarrow[]{L^1} h(s)$.
    The second limit is zero because of the continuous mapping theorem, as $S_n \xrightarrow[]{p} S$ and $\Pr_S(s : r\text{ is not continuous at }s)= 0$.

@@

\subsection{Weighted value}

Let us now examine the weighted value in the multi-sided case.
The set of players and the characteristic function are the same as in the previous section, but players have the following weights: player $P$ has weight $\lambda_P$, while players $A^l_i$ have weight $\lambda_l$.
I will show, that as with the Shapley-value, the limit of the weighted value can also be expressed as an integral over a one-dimensional path.
However, this path is not the diagonal of the unit hypercube, and depends on the ratio of the fringe players' weights.

\begin{proposition}
    \label{prop:many_sided_weighted}
    Let $f$ be continuous on $[0, 1]^L$.
    Then,
    \begin{align*}
        \varphi_P^\infty & = \int_0^1 f(t^{\lambda_1}, \dots, t^{\lambda^L}) \lambda_P t^{\lambda_P} \dt.
    \end{align*}
\end{proposition}

\begin{proof}[Proof of \cref{prop:many_sided_weighted}]
    The proof uses the same approach as that of \cref{prop:many_sided_shapley}.
    I will show that $X_n \xrightarrow[]{d} h(\xi)$, where $h(s) = (s^{\lambda_1}, \dots, s^{\lambda_L})$, and $\xi$ is a random variable with cdf $G(s) = s^{\lambda_P}$, and then rely on \cref{lem:many_sided_manifold}.

@@

\begin{lemma}
    \label{lemma:log_convergence}
    Let 
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n}, \\
        \Delta(s) &= \frac{1}{s}.
    \end{align*}
    Then $\Delta_n \xrightarrow[]{\mathrm{u}} \Delta$ uniformly on $[t, 1]$ for any $t > 0, \lambda > 0$.
\end{lemma}
\begin{proof}[Proof of \cref{lemma:log_convergence}]
    First, note that $\Delta_n$ and $\Delta$ are all continuous functions.
    Then, following the standard proof for $\frac{\mathrm{d}}{\mathrm{d}s}log(s) = \frac{1}{s}$ rewrite $\Delta_n(s)$ as
    \begin{align*}
        \Delta_n(s) &= \frac{\log(s + 1/n) - \log(\lambda)}{n} \\
        &= \log \left( 1 + \frac{1}{sn} \right) ^ n .
    \end{align*}
    It is well known that $\left( 1 + \frac{1}{sn} \right) ^ n$ is monotone increasing in $n$ and converges to $\exp (1/s)$.
    Therefore, the pointwise convergence of $\Delta_n(s) \to \Delta(s)$ is also monotone.

@@

\begin{lemma}
    \label{lemma:integral_convergence}
    Let $f_n, f: [a, b] -> \mathbb{R}$ be Riemann-integrable functions with $f_n \xrightarrow[]{\mathrm{u}} f$ uniformly.
    Then,
    \begin{align*}
        \lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) = \int_0^1 f(t) \dt.
    \end{align*}
\end{lemma}
\begin{proof}[Proof of \cref{lemma:integral_convergence}]
    \begin{align*}
        &\lim_{n \to \infty} \frac{b-a}{n} \sum_{k=1}^n f_n \left( a + \frac{b-a}{n} \right) \\
        &= \lim_{n \to \infty} \frac{b-a}{n} \left[ \sum_{k=1}^n f \left( a + \frac{b-a}{n} \right) + \sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \right] \\
        &= \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left( f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right) \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \left| f_n \left( a + \frac{b-a}{n} \right) - f \left( a + \frac{b-a}{n} \right) \right| \\
        &\leq \int_a^b f(t) \dt + \lim_{n \to \infty} \frac{b-a}{n}\sum_{k=1}^n \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right| \\
        &= \int_a^b f(t) \dt + (b-a) \underbrace{\lim_{n \to \infty} \sup_{t \in [a, b]} \left| f_n(t) - f(t) \right|}_{=0 \text{ due to uniform convergence}} \\
        &= \int_a^b f(t) \dt
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of \cref{prop:monotone}]
    Monotonicity is evident.
    For superadditivity, note that for any coalitions $S_1, s_2$ such that $S_1 \cap s_2 = \emptyset$, $P \notin S_1$ or $P \notin s_2$.
    WLOG assume it is the latter, therefore $v(S_2) = 0$.
    As a result, $v(S_1) + v(S_2) = v(S_1) \leq v(S_1 \cup S_2)$ holds if and only if $(N, v)$ is monotone.
\end{proof}

\begin{proof}[Proof of \cref{prop:one_sided}]
    Let $R$ denote a permutation of the set of players ($N$).
    Additionally, let us denote the players preceding $i$ by $\mathcal{P}_i^R$.
    The value of player $P$ is their expected marginal contribution averaged over all permutations of $N$:
    \begin{align*}
        \varphi_P^n = \frac{1}{(n+1)!} \sum_R v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)
    \end{align*}
    First, note that $v(\mathcal{P}_P^R) = 0$ for any permutation, as no coalition can achieve a positive value without player $P$.
    Furthermore, using the fact that all agents of type $A$ are identical implies that $v(\mathcal{P}_P^R \cup \{i\})$ only depends on the number of agents in the coalition.
    More precisely, 
    \begin{align*}
        v(\mathcal{P}_P^R \cup \{i\}) = f(n_A(\mathcal{P}_P^R \cup \{i\}) / n) = f(|\mathcal{P}_P^R| / n).
    \end{align*}
    Finally, the set of permutations in which $k$ number of players precede $P$ is independent of $n$, i.e.
    \begin{align*}
        \{R \mid |\mathcal{P}_P^R| = k\} = n! \quad \forall\, k.
    \end{align*}
    Putting all the above together, the value of player $P$ can be expressed as
    \begin{align*}
        \varphi_P^n &= \frac{1}{(n+1)!} \sum_{k=0}^n n! f(k / n) \\
        &= \frac{1}{n+1} \sum_{k=0}^n f(k / n) \\
        &= \frac{n}{n+1} \underbrace{\frac{1}{n} \sum_{k=0}^{n-1} f(k / n)}_{=S_n} + \frac{1}{n+1} f(1).
    \end{align*}
    $S_n$ are just the left Riemann-sums of function $f$ on the interval $[0, 1]$.
    Therefore, if $f$ is continuous (and thus Riemann-integrable), then $S_n \to \int_0^1 f(t)$, and thus
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^n &= \lim_{n \to \infty} \frac{1}{n+1} \sum_{k=1}^n f(k / n) \\
        &= \lim_{n \to \infty}\underbrace{\frac{n}{n+1}}_{\to 1} \frac{1}{n} \sum_{k=0}^{n-1} f(k / n) + \underbrace{\frac{1}{n+1} f(1)}_{\to 0} \\
        &= \int_0^1 f(t) \dt .
    \end{align*}
\end{proof}

@@

\begin{proof}[Proof of \cref{lem:entry_distr}] %\textcolor{red}{(Might have to fix sum indices)} \\
    The probability of $P$ having at most fraction $t$ of the other players before itself is
    \begin{align*}
        \Pr(X_n \leq nt) &= \Pr(X_n \leq nt ) \\
        &= \prod_{j = nt + 1}^n \frac{j}{j + \lambda} \\
        &= \exp \Bigg( \underbrace{\sum_{j = nt + 1}^n \log(j) - \log(j+\lambda)}_{\equiv S_n} \Bigg).
    \end{align*}
    Taking limits,
    \begin{align*}
        \lim_{n \to \infty} S_n &= \lim_{n \to \infty} \sum_{j = nt + 1}^n \log(j) - \log(j+\lambda) \\
        &= \lim_{n \to \infty} \sum_{i = 1}^{n - nt} \log(nt + i) - \log(nt + i + \lambda) \\
        &= \lim_{n \to \infty} \frac{1}{n - nt} \sum_{i = 1}^{n - nt} \frac{\log \left( t + \frac{i}{n - nt} \right) - \log \left( t + \frac{i}{n - nt} + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    Let
    \begin{align*}
        \Delta_n(s) = \frac{\log \left( s \right) - \log \left( s + \frac{\lambda}{n - nt} \right)}{1 / (n - nt)}
    \end{align*}
    By lemma \ref{lemma:log_convergence}, 
    \begin{align*}
        \Delta_n \xrightarrow[]{\mathrm{u}} \lambda \frac{\mathrm{d}}{\mathrm{d}s}log(s) = -\frac{\lambda}{s}
    \end{align*}
    on the compact interval $[t, 1]$ for any $t > 0$ ($\xrightarrow[]{\mathrm{u}}$ denotes uniform convergence).

@@

\begin{proof}[Proof of \cref{prop:one_sided_weighted}]
    The weighted value of player $P$ is its expected contribution across all permutations, with each permutation weighted by its probability of occurring.
    \begin{align*}
        \varphi_P^{n, \lambda} = \sum_R \Pr(R) [v(\mathcal{P}_P^R \cup \{i\}) - v(\mathcal{P}_P^R)]
    \end{align*}
    As before, using the fact that fringe players are identical, this can be rephrased as
    \begin{align*}
        \varphi_P^{n, \lambda} &= \sum_{k=0}^n \Pr(R) f(k/n) \\
        &= \E[f(X_n / n)]
    \end{align*}
    where $X_n$ is defined as above.
    $f$ is continuous, and therefore bounded on the compact set $[0, 1]$.
    As a consequence, $\frac{X_n}{n} \xrightarrow[]{d} X$ implies $\E[f(X_n / n)] \to \E[f(X)]$, which in turn gives
    \begin{align*}
        \lim_{n \to \infty} \varphi_P^{n, \lambda} &= \lim_{n \to \infty} \E[f(X_n / n)] \\
        &= \E[f(X)] \\
        &= \int_0^1 f(t) \mathrm{d}G(t) \\
        &= \int_0^1 g(t)f(t) \dt
    \end{align*}
    where $G(t)$ and $g(t)$ are the cdf and pdf of X, respectively.
\end{proof}
